# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

## Exercise 1 

### R built-in functions... fun with R 

R provides numerous built-in functions and variables. For each line below, type the test in the Console to see what happens. Is the result what you expect? Fill in the blanks with the screen output for the line. 
```{r}
#This is a comment -- no action is executed by the computer. 
```

Variables, constants, and simple calculations: 

```{r Variables, constants, simple calculations}
a <- 100 #Look at the Global Environment. A VARIABLE called a has been created

a <- 101 #Look at the variable's value in the Global Environment
b <- 99
a/b            # __________________________
x <- 2 
y <- x^x       # __________________________

z <- y^y       # __________________________

```

Built-in functions: 

```{r Built-in functions}
sqrt(x)       # ___________________________
pi  # pi is a built-in variable in R 
cos(pi)       # ___________________________

abs(cos(pi))  # ___________________________

# How can we make this line of code simpler? 
#By assigning the answer to a variable! 

x <- cos(pi)
abs(x)      # __________________________

exp(x)      # __________________________

# In Math, how do you write exp(x)? _________________

b <- (4*2)
```
